Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2018-12-05 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r3.tex
paper update

\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $, $ T_{ref}=25^{o}C $), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time. Mathematically, it is the ratio between the present capacity and the nominal capacity (in $ Ah $, provided by manufacturer). If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
%\begin{equation}
%\label{eq:SOCbat}
%SOC = \left( 1 - \dfrac{Q}{C} \right) 
%\end{equation}
%
%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
%
%The ratio between $ Q $ and $ C $ represents t
The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.

%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}. This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
%
%\begin{equation}
%\label{eq:CC10}
%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
%\end{equation}
%
%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.

For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
%
\begin{multline}
\label{eq:Vcbat}
V_{c} = [2+0.16SOC]+ \\ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
\end{multline}

@@

\noindent where the variable $autonomy$ is a design definition and normally has a value ranging from $6$ to $48$h; the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.

>>>>

\noindent where $C_{10}$ means 10h of rated capacity, which is standard on the manufacturer's data-sheet, $\Delta T$ is temperature variation ($\Delta T=T-T_{ref} $%, $ T_{ref}=25^{o}C $
), $ SOC $ or state of charge indicates how much electric charge is stored in the cell at a given time. Mathematically, it is the ratio between the present capacity and the nominal capacity% (in $ Ah $, provided by manufacturer)
. If $SOC=1$, then the battery is totally charged; and if $ SOC=0 $, then the battery is fully discharged.  %, defined by Equation \ref{eq:SOCbat}.
%\begin{equation}
%\label{eq:SOCbat}
%SOC = \left( 1 - \dfrac{Q}{C} \right) 
%\end{equation}
%
%Where $ Q $ is the charge delivered at the time of interest ($ Q=It $), and C is the battery capacity.
%
%The ratio between $ Q $ and $ C $ represents t
The depth of discharge ($DOD$) or the fraction of discharge, is $DOC=1-SOC$.

%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}. This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
%
%\begin{equation}
%\label{eq:CC10}
%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
%\end{equation}
%
%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
%
\begin{multline}
\label{eq:Vcbat}
V_{c} = [2+0.16SOC]+ \\ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
\end{multline}

@@

\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
the other variables were discussed previously in Section~\ref{sec:PVmodel} and ~\ref{sec:BATmodel}.
